Exploring dimensions of biodiversity in Japanese ferns

### 2021-04-23 ms/manuscript.Rmd
Update MS

tar_load(c(
  "occ_point_data_ferns",
  "occ_point_data_ferns_unfiltered",
  "biodiv_ferns_spatial",
  "k_taxonomy",
  "k_phylogeny",
  "signif_cells_protected_area",
  "protected_areas",
  "japan_shp",
  "phy_sig_results",
  "binary_sig_results",
  "traits_summary",
  "fern_traits",
  "japan_pterido_tree",
  "japan_fern_tree",
  "ppgi",
  "occ_point_data_ferns",
  "comm_ferns_full",
  "comm_ferns",
  "japan_points_raw",
  "green_list"
))

phylo_cache <- drake::new_cache(here::here("phylo_cache"))

drake::loadd(list = c(
  "plastome_calibration_dates",
  "plastome_tree"
),
cache = phylo_cache)

@@

The ferns of Japan are excellent model system because they have been the target of intense botanical interest for several decades and are densely sampled. One particularly valuable characteristic of this flora is the availability of data on reproductive mode (known for 221/721 taxa [70%]), which is likely to effect genetic diversity [@Bengtsson2003], and thereby higher-level biodiversity [@Krueger-Hadfield2019]. Japan is situated along a latitudinal gradient spanning highly season temperate areas in the north to subtropical, mostly aseasonal islands in the south.

@@

@@

```{r phy-sig-stats}
# Verify that min lambda >0.95
assert_that(phy_sig_results %>% pull(lambda) %>% min > 0.95)
# Verify that max K < 0.0.6
assert_that(phy_sig_results %>% pull(kval) %>% max < 0.06)

@@

All continuous traits showed significant phylogenetic signal, but estimates of signal strength differed between *K* and lambda: all lambda values were > 0.95, indicating evolution by BM; however, values of *K* were < 0.06, indicating less phylogenetic signal than expected under BM (`r s_table("phy-sig")`). `r n_negative_d` out of `r nrow(binary_sig_results)` of continuous traits (coded as binary) showed as much or more phylogenetic signal as expected under BM (*D* =< 0); others had *D* > 0 (`r s_table("phy-sig-binary")`).

>>>>

tar_load(c(
  "occ_point_data_ferns",
  "occ_point_data_ferns_unfiltered",
  "biodiv_ferns_spatial",
  "k_taxonomy",
  "k_phylogeny",
  "signif_cells_protected_area",
  "protected_areas",
  "japan_shp",
  "phy_sig_results",
  "binary_sig_results",
  "traits_summary",
  "fern_traits",
  "japan_pterido_tree",
  "japan_fern_tree",
  "ppgi",
  "occ_point_data_ferns",
  "comm_ferns_full",
  "comm_ferns",
  "japan_points_raw",
  "plastome_calibration_dates",
  "plastome_tree",
  "green_list"
))

@@

The ferns of Japan are excellent model system because they have been the target of intense botanical interest for several decades and are densely sampled. One particularly valuable characteristic of this flora is the availability of data on reproductive mode (known for 221/721 taxa [70%]), which is likely to affect genetic diversity [@Bengtsson2003], and thereby higher-level biodiversity [@Krueger-Hadfield2019].

Japan is situated along a latitudinal gradient spanning highly season temperate areas in the north to subtropical, mostly aseasonal islands in the south. Furthermore, it is a mountainous country with great variation in elevation on the larger islands. Plant distributions often reflect physiological adaptations to climate (e.g., percipiation and temperature). Therefore, we expect the spatial distribution of biodviversity to be determined by climatic variation in addition to reproductive mode.

@@

### Climate data

We downloaded climate data at the 2.5 minute scale from the WorldClim database using the `getData` function in the R package `raster`, and extracted four variables related to our research questions as follows: mean annual temperature (bio1), temperature seasonality (bio4), annual precipitation (bio12), and precipitation seasonality (bio15). We checked for correlation between climatic variables while taking into account spatial autocorrelation using a modified *t*-test with the `modified.ttest` in the `SpatialPack` R package; as a result, we excluded temperature seasonality, which was correlated with mean annual temperature. We identified the intersection of the climate data at the 2.5 minute scale with the 0.2° grid-cells, then calculated the mean of each climatic variable for each 0.2° grid-cell. The R package 'sf' was used for GIS analyses.

@@

```{r phy-sig-stats}
# Verify that min lambda >0.95
# assert_that(phy_sig_results %>% pull(lambda) %>% min > 0.95)
# Verify that max K < 0.0.6
# assert_that(phy_sig_results %>% pull(kval) %>% max < 0.06)

@@

<!-- All continuous traits showed significant phylogenetic signal, but estimates of signal strength differed between *K* and lambda: all lambda values were > 0.95, indicating evolution by BM; however, values of *K* were < 0.06, indicating less phylogenetic signal than expected under BM (`r s_table("phy-sig")`). `r n_negative_d` out of `r nrow(binary_sig_results)` of continuous traits (coded as binary) showed as much or more phylogenetic signal as expected under BM (*D* =< 0); others had *D* > 0 (`r s_table("phy-sig-binary")`). -->
